Population Inference of Eccentric Binary Black Holes

### 2023-05-23 paper/paper.tex
Updates from Overleaf

    \item to compute the $\mu(\mathcal{R},\Lambda)$, we use previously defined Volume in $Gpc^{-3}yr^{-1}$ and observing at this senstivity for the time $T$, the average number of detections would be as follows: \\
\begin{equation}
\label{eq:mu}
  \mu(\mathcal{R},\Lambda) = \int(VT)\lambda \mathcal{R}p(\lambda|\Lambda)d\lambda  
\end{equation}
    \item where $p(\lambda|\Lambda)$ is the probability density function for a random binary in the universe to have intrinsic paramter $\lambda$. Keep in mind that $\lambda$ is equal to all the 15 parameters of a binary.
\end{itemize}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

>>>>

    \item to compute the $\mu(\mathcal{R},\Lambda)$, we use previously defined Volume in $Gpc^{-3}yr^{-1}$ and observing at this sensitivity for the time $T$, the average number of detection would be as follows: \\
\begin{equation}
\label{eq:mu}
  \mu(\mathcal{R},\Lambda) = \int(VT)\lambda \mathcal{R}p(\lambda|\Lambda)d\lambda  
\end{equation}
    \item where $p(\lambda|\Lambda)$ is the probability density function for a random binary in the universe to have intrinsic paramter $\lambda$. Keep in mind that $\lambda$ is equal to all the 15 parameters of a binary.
\end{itemize}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop3d038.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop2d038.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop2d038scl.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}
\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/pop2d038diff.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}
\begin{figure}
\includegraphics[width=0.45\textwidth]{paper/figures/massloss038.png}
\caption{\label{fig:population05}\textbf{Synthetic Population of Eccentric BBHs}}
\end{figure}
